Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-30 manuscript/manuscript.Rmd
typo

As can be expected, the dynamics of eq. \eqref{eq:3d model} are significantly more complex than those of eq. \eqref{eq:may}.
There are a variety of fixed points for the equations---around 8 or 9 for wide ranges of parameter values.
Fig. \ref{fig:tbd} provides a rough idea of the fixed point structure by plotting the bifurcation diagram obtained from varying $c_{XY}$ and fixing the other parameters.

>>>>

As can be expected, the dynamics of eq. \eqref{eq:3d model} are significantly more complex than those of eq. \eqref{eq:may}.
There are a variety of fixed points for the equations---around 8 or 9 for wide ranges of parameter values.
Fig. \ref{fig:tbd} provides a rough idea of the fixed point structure by plotting the bifurcation diagram obtained from varying $D$ and fixing the other parameters.
